A unified pseudo-$C_\ell$ framework

### 2018-08-31 doc/Paper/main.tex

>>>>

      \subsubsection{Pixelization and signal band-limits}

      SHT transforms as written in the Eq.~\ref{eq:sht1} is, strictly
      speaking, defined on a continuous field on the sky and results
      in an infinite number of spherical harmonic coefficients. In
      practice, we have to always deal with a finite number of pixels
      at which the field is sampled and consequently use a finite
      number of spherical coefficients. If the sampling of the
      underlying signal is too sparse, one will get aliasing of higher
      frequency modes. In flat spaces, Nyquist theorem provides a
      clear prescription for uniform sampling on a grid. Since there
      is no such natural sampling on a sphere, the situation is more
      complex and depends on the pixelization scheme
      \cite{Driscoll:1994:CFT:184069.184073,
        DBLP:journals/corr/abs-1110-6297}. Nevertheless, clear
      heuristic prescriptions exist. Most importantly, the pixel separation needs
      to be smaller than the wavelength of the highest frequency
      present in the underlying signal. As a natural consequence, the
      smoothing of the map must always precede any downgrade in
      resolution (or equivalently downsampling) if it is necessary to
      do so for numerical expediency.  Similarly, any mask should be
      applied at the highest possible resolution and the resulting
      map smoothed before being down-graded.

      For the same reasons, even if the signal is correctly sampled in
      a band-limited fashion, one must always estimate power over the
      entire power band, even if one is not interested in certain
      region of $\ell$ space. Otherwise, the power spectrum estimator
      will try to ``explain'' the variance associated with $\ell$
      modes not considered by artificially inflating the power in the
      estimated modes. For {\tt HEALPix} \citep{2005ApJ...622..759G}
      pixelization commonly used in cosmology and also in this paper,
      \cite{2013MNRAS.435.1857L} suggest the following
      prescription. If one wants to measure power up to $\ell_{\rm
        max}$, one should employ pixelisation of
      \texttt{Nside}=$\ell_{\rm max}/2$ and estimate band-powers up
      to $2 \ell_{\rm max}$, but then discard measurements above $\ell_{\rm
        max}$ after correcting for pixel-response suppression and
      accounting for their contribution to the covariance matrix of
      measurements.

      In this paper we do not consider these issues any further as \nmt
      is a generic tool and it is up to the user to ensure band-limit
      and pixelization constraints are properly accounted for.
